% Resume build on 11th Nov.
% Need any help in modification,contact the mentioned URL
% \href{https://praveen-yadav.github.io/}{Github}
\documentclass{resume}
\usepackage[T1]{fontenc}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
% 3 lines for changing any hyperlink to dark blue color so that printout time it wont make any color difference but on PC it will look different.
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

\name{PRAVEEN K. YADAV}
\address{\emph{sudomailpraveen@gmail.com} \addressskip | \emph{+91-9705450431} | \emph{\href{https://www.linkedin.com/in/praveen-yadav-7a9b2b80/}{linkedin}}}

\begin{document}
 
\begin{rSection}{\header{Work Experience}{}}
%------------------------------------------------
\begin{rSubsection}{Senior Software Engineer, Qualcomm Inc. Hyderabad}{\emph{Jul'17- Sep'20}}{}{} 
\item Role: Development and commercialization of \textbf{Location Middleware }software, inside GPS modem. This layer uses various network protocols(SUPL/LPP/LPPe/WIFI/WWAN) and Location Engine(GPS) to compute and share the position fix with concurrent android clients. [Software Eng./C++/C]
\\
\item Feature: Redesign state-machine of location service, to satisfy less memory and power constraint of {\href{https://www.qualcomm.com/products/qualcomm-9205-lte-modem}{\textbf{IoT modem}}}

\item Took initiative of creating a log-playback tool which helped in simulation of customer test scenarios from the logs. 
\end{rSubsection} 
%------------------------------------------------
%------------------------------------------------
\begin{rSubsection}{Engineer, Arista Networks, Bengaluru [*]}{\emph{Oct'20- current}}{}{} 
\item Role: Worked on Extended Operating System (OS which runs on commerical Networking switch) . Added Feature which involves setting custom Cos-to-Tc and DSCP-To-TC maps per subInterfaces . Started from networking 101, but gained good knowledge of networking.  [Software Eng./C++/Python/TACC]
\end{rSubsection} 
%------------------------------------------------
\end{rSection} 


\begin{rSection}{\header{Projects}{}}
%------------------------------------------------
\begin{rSubsection}{\href{https://github.com/somename058/IAS_DataListener}{Internet of Things(IoT) Applications Platform as a Service}}{}{}{} 
\item Built a generic end-to-end platform that handles the storage, processing and delivery of the IoT data from sensors to the mobile apps.
 [NodeJS,MongoDB]
 \end{rSubsection} 

%------------------------------------------------
\begin{rSubsection}{Search Engine for Huge Wikipedia corpus}{}{}{}
\item Using NLP and indexing techniques, able to query 63GB wiki dump and retrieve the top 10 matching Wikipedia documents within 1 seconds. Supports field search on - title, Infobox, text, categories. [Indexing,NLP,Java]
\end{rSubsection}


%------------------------------------------------
\begin{rSubsection}{\href{https://github.com/praveen-yadav/express_with_react}{Emaily - A User Feedback Web Application}}{\emph{Aug 2020 }}{}{}
\item 
Allow client to send customized surveys via email and record user-feedback with web-hooks and {\href{https://powerful-caverns-04805.herokuapp.com/r}{deployed on Heroku}}
With this project, I wanted to do hands-on with payments, authentication(GoogleOAuth) and redux.

Used Stripe for Payment Processing and buying credits; 
SendGrid for sending emails and recording user responses;
Using Redux to store application state inside browser.  [Mongo/Express/React/Node]
\end{rSubsection}


\iffalse
%------------------------------------------------
\begin{rSubsection}{Index real-time Twitter stream }{\emph{2019 }}{}{}
\item Insert real-time tweets into Kafka-topic. Consumers take data from Kafka and put it in Elastic-Search for indexing. [Distributed system, Apache Kafka]
\end{rSubsection}
%------------------------------------------------
\fi

\end{rSection} 

%------------------------------------------------Mini Projects are comment out------------------%
\iffalse
\begin{rSectionlight}{\header{Mini Projects}}
% ------------------------------------------------
\begin{rSubsectionmini}{HTTP Proxy Cache Server}{}{}{}
\item Cache the HTTP Requests,Responses and Resources. Support blacklisting websites [C,Pthread,HTTP]
\end{rSubsectionmini}
%------------------------------------------------
\begin{rSubsectionmini}{Shell Implementation}{}{}{}
\item Key: Support for I/O direction,Linux Pipes,Background and foreground functionality : \&, fg [C++]
\end{rSubsectionmini}
%------------------------------------------------
\end{rSectionlight}
\fi
%------------------------------------------------Mini Projects are comment out------------------%


\begin{rSectionlight}{\header{Education}{}}
\vspace{6pt}
{\bf  M.Tech. in Computer Science} \hfill 7.67/10.00 |  {\emph{Aug. 2015 - May 2017}}\\ 
\emph{International Institute of Information Technology, Hyderabad.} \\
{\bf B.Tech. in Computer Science} \hfill 7.78/10.00 | {\emph{Aug. 2011 - May 2015}}\\
\emph{Jabalpur Engineering College, Jabalpur.} \\
{ CBSE Class XII \hfill } 87.60\% | {\emph{Apr. 2010 - Mar 2011}}
%--{\bf SSC, Class X CBSE}  \hfill  88.80\% | {\emph{Apr. 2008 - Mar 2009}}\\
%--Kendriya Vidyalya CMM,Jabalpur, M.P. 
\end{rSectionlight}

\begin{rSectionlight}{ \header{Skills And Interests}{}}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & C and C++ \{Proficient\}, Python, Java .\\
%--, 
Technologies & ReactJS, NodeJS, SQL, Git, Perforce, Bash Scripting
\\
\end{tabular}
\end{rSectionlight}


\begin{rSectionlight}{
\header{Scholastic and Extra-Curricular Achievements}{}
}  
\smallskip
{All India Rank 902 in GATE-2015 out of more than 1,55,000 students. \hfill \emph{2015}}\\
Awarded Merit Scholarship under Education Scholarship Scheme for Army (ESSA) \hfill \emph{2012, 2013}\\
\end{rSectionlight}


\end{document}
